Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-02 Paper/main.tex
small typo
Added conclusion

\section{Conclusion}
Put conclusion here.

@@

The authors wish to acknowlege the contributions from M. Churchfield
and S. Yellapantula for their development of the LES boundary
conditions and for their efforts in validating the ExaWind codes.

>>>>

\section{Conclusion}
In this study we have simulated the stable offshore boundary layer
matching the characteristics of measurements from Nantucket Sound in
the Northeastern US.  Three cases with wind speeds of 5 m/s, 10 m/s,
and 15 m/s were selected, and simulations were performed using the
ExaWind codes to match the TI and stability levels observed at from
the Cape Wind platform.  When examining the effect of stratification
using the Obukhov length, differences in the ABL behavior were seen
bewteen the very stable boundary layer cases (5 m/s and 10 m/s), and
the stably stratified case (15 m/s).  The very stable cases had
shorter turbulent structures and less growth in the boundary layer
compared to the 15 m/s case.  The behavior of the three stable
boundary layers was also compared to the neutral and unstable cases
studied in \cite{cheung2020large}.  As expected, the turbulent
structures in all stable cases were noticeably smaller than in the
neutral and unstable boundary layers.

In addition to these simulations, we also examined the domain and mesh
requirements necessary for the stable offshore boundary layers
considered here.  Based on the calculated turbulent integral
lengthscale, horizontal domain sizes of 750m $\times$ 750m were found
to be necessary for these simulations.  Various mesh resolutions were
also considered for the stable runs, and it was determined that the
finest resolution of $dx$=2.5m was able to resolve the longitudinal
length scales and highest temporal frequencies, but inadequate for
resolving the turbulence in the lateral direction.  Further study is
warranted to comprehensively determine the impact of stable
stratification on the required mesh resolution.

Lastly, a comparison of the ExaWind solvers Nalu-Wind and AMR-Wind was
conducted using the stable offshore boundary layer at 5 m/s.  The mean
statistics were found to agree well between the two LES codes.  Small
differences were found in wind profiles at higher elevations and for
the peak $S_u$ spectra, and excellent matches were observed for the
averaged veer, temperature, and TI profiles.

@@

The authors wish to acknowledge the contributions from M. Churchfield
and S. Yellapantula for their development of the LES boundary
conditions and for their efforts in validating the ExaWind codes.
